### 2019-05-23 README.Rmd
Fix spacing issues on GitHub
Major update to the README to reflect recent changes as part of V0.2.0

<br>

## Description
**UPDATE**: `robvis` now exists as a [web-app](https://mcguinlu.shinyapps.io/robvis), aimed at those who are not confident with R/those who want to explore the package's functionality.

The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, produces a summary plot (incorporating some measure of weighting for each study), and formats the plot according to the assessment tool used.

The package contains three functions:

### rob_summary()
Returns a ggplot object displaying a weighted barchart of the risk of bias of included studies across the domains of the specified tool.

### rob_traffic_light()
Returns a ggplot object displaying a ["traffic light plot"](https://handbook-5-1.cochrane.org/chapter_8/figure_8_6_c_example_of_a_risk_of_bias_summary_figure.htm), displaying the risk of bias judgement made in each domain for each study.

### rob_tools()
Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary(). Users can currently produce summary plots for three commonly used tools: ROB2.0, ROBINS-I and QUADAS-2. We expect this list to be updated in the near future to inlcude tools such as ROBIS (tool for assessing risk of bias in systematic reviews).

    rob_tools()
    [1] "ROB2"
    [1] "ROBINS-I"
    [1] "QUADAS-2"

## Getting started
### Install the `robvis` R package
First ensure you have the `devtools` package installed:

@@

### Load data
Load your own data (mostly likely from a .csv)

@@

To familiarise users with the package, we have included three example datasets, one for each fo the tool templates that currently exist within `rob_summary()`. These datasets are used to create the example plots below.

### Create basic plots
```{r include = FALSE}
library(robvis)
```

#### RoB2.0 tool for randomized controlled trials:
```{r}
plot_rob <- rob_summary(data = data_rob, tool = "ROB2")
plot_rob
```

```{r out.width = "90%", fig.width= 8, fig.height=8}
trafficlight_rob <- rob_traffic_light(data = data_rob, tool = "ROB2")
trafficlight_rob
```

#### ROBINS-I tool for non-randomised studies of interventions:**
```{r}
plot_robins <- rob_summary(data = data_robins, tool = "ROBINS-I")
plot_robins
```

#### QUADAS-2 tool for diagnostic accuracy studies:**
```{r}
plot_quadas <- rob_summary(data = data_quadas, tool = "QUADAS-2")
plot_quadas
```

## Additional usage
Because the output (`plot_tool` in the above examples) is a ggplot2 object, it is easy to adjust the plot to your own preferences.

For example, to add a title to the RoB2.0 plot created above:
```{r warning=FALSE}
library(ggplot2)

plot_rob +
  ggtitle("Summary of RoB2.0 assessments")
```

## Planned updates

* Templates for additional risk of bias tools, including:
  * Cochrane risk of bias tool for randomised controlled trials (RoB Version 1)
  * PROBAST
  * ROBIS
* Ability to specify file type extension when saving image. Priority being Window 
* Additional functionality to specify the element of QUADAS-2 that you want to visualise (applicability or risk of bias)
* Choice of colour schemes (or ability to specify your own colours, have not decided yet)
* Improved text processing to allow for imperfect matching of judgements, primarily to allow for differences in cases (e.g. "low" will match with "Low"" and for minor spelling errors (e.g. "loq" will match with "Low")
* A planned function to provide a brief draft paragraph summarising the risk-of-bias assessment results, which authors can then edit/elaborate on as needed. This element of the project was inspired by the reporter function in `metafor`

>>>>

**UPDATE**: `robvis` now exists as a [web-app](https://mcguinlu.shinyapps.io/robvis), aimed at those who are not familiar with R or who want to explore the package's functionality before installing it locally.

## Description
```{r include = FALSE}
library(robvis)
library(kableExtra)
library(magrittr)
```
The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, and produces summary plots formatted according to the assessment tool used.

## Getting started
### Install the `robvis` pacakage
First ensure you have the `devtools` package installed:

@@

### Load data
To load your own data from a .csv file:

@@

To help users explore `robvis`, we have included example datasets in the package, one for each fo the tool templates that currently exist within `rob_summary()`. The `data_rob2` dataset ([view it here](https://github.com/mcguinlu/robvis/blob/master/data_raw/data_rob2.csv)), which contains example risk-of-bias assessments performed using the RoB2.0 tool for randomized controlled trials, is used to create the plots in subsequent sections.

### Create plots

The package contains two plotting functions:

#### 1. rob_summary()
Returns a ggplot object displaying a weighted barchart of the risk of bias of included studies across the domains of the specified tool.

```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2")
summary_rob
```

#### 2. rob_traffic_light()
Returns a ggplot object displaying a ["traffic light plot"](https://handbook-5-1.cochrane.org/chapter_8/figure_8_6_c_example_of_a_risk_of_bias_summary_figure.htm), displaying the risk of bias judgement in each domain for each study.

```{r eval=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
trafficlight_rob
```    
<img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/>

### Other functions
#### rob_tools()
Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary(). We expect this list to be updated in the near future to inlcude tools such as ROBIS (tool for assessing risk of bias in systematic reviews).

    rob_tools()
    [1] "ROB2"
    [1] "ROBINS-I"
    [1] "QUADAS-2"
    [1] "ROB1"

## Advanced usage
### Change the colour scheme
The `colour` argument of both plotting functions allows users to select from two predefined colour schemes ("cochrane" or "colourblind") or to define their own pallete by providing a vector of hex codes.

For example, to use the predefined "colourblind" palette:

```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", colour = "colourblind")
summary_rob
```

And to define your own colour scheme:
```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", colour = c("#f442c8","#bef441","#000000"))
summary_rob
```

### Created an unweighted summary barplot:
By default, the `rob_summary()` function creates a barplot weighted by some measure of a study's precision. This can be prevented using the "weighted" argument. For example, compare the following two plots:

```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2")
summary_rob
```

```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", weighted = FALSE)
summary_rob
```

### Editing the plots
Finally, because the output (`summary_rob` and `trafficlight_rob` in the examples above) is a ggplot2 object, it is easy to adjust the plot to your own preferences.

For example, to add a title to the unweighted RoB2.0 plot created above:
```{r warning=FALSE, fig.height=3}
library(ggplot2)

summary_rob +
  ggtitle("Summary of RoB2.0 assessments")
```
